\name: Deterministic and Coherent Implicits

### 2018-06-07 src/DesignChoices.tex
Starting my revisions
Local changes

\begin{code}

data IntSet = C a deriving Eq

class C a where
  m :: a -> a

instance Eq a => C [a] where

instance Ord a => C [a] where

fun :: StablePtr Int -> [StablePtr Int]
fun sp = m [sp]

\end{code}

@@

@@

\begin{code}

\end{code}

@@

>>>>

> data IntSet = C a deriving Eq
> 
> class C a where
>   m :: a -> a
>
> instance Eq a => C [a] where
> 
> instance Ord a => C [a] where
> 
> fun :: StablePtr Int -> [StablePtr Int]
> fun sp = m [sp]

@@

A few concerns are:

1) open vs closed world. In open world you could add more instances, so you don't know whether your choice is unique or the best
2) reasoning: if you backtrack then programmers have to follow the backtracking reasoning, which can be complex for more involved instance declarations
3) performance: You may pay significant penalties at compile time by backtracking

@@

>

@@

special treatment of superclasses:

compute the closure of all given superclasses before resolution

-> treat that closure like other givens

 when matching, try to match the givens first, because they are non-recursive

-> if none of the givens work, try global instances
